\chapter{Related Work}

The importance of video service in the cloud is considerable due to lot amount of video information transferred over networks. Recently, video cloud has become a hot research topic. The compressed video sensing and sparse representation is an alternative that is gaining strength thanks to the results of compressive sensing in fields as image/video reconstruction, image/video super-resolution and image/video compression. For video coding with sparse representation, Shen et al. in \cite{motion_cs} propose to perform the motion estimation based in sparse representation. A region $C$ denotes the current block to  be predicted and a region $S$ denotes the neighbour blocks of $C$.  search a good approximation for know pixels in a $S$ region and its sparse representation coefficient is calculated and then keep the same procedure to estimate the unknown pixel value in $C$ region. In this proposal two dictionary are used, $D_S$ for pixel of region $S$ and $D_C$ for pixel of region $C$. Sparse representation is calculated with OMP algorithm and energy of residual on the current block is used as the stopping criteria. In \cite{odl_me}, Sun et al. propose a framework for inter-frame video coding using sparse representation with online dictionary learning. The dictionary is training with textured patches of each frame in the video in order to obtain sparse representation for the following frames. Furthermore, the sparse coefficients are quantized and encoded using Huffman entropy encode. A module is added in the encoder for construct the sparse representation and another is added the decoder for reconstruct the image. The framework was compared with H.264 video encoder and  K-SVD dictionary, showing better rate distortion performance but increasing the bit rate the performance gradually decrease. \\

For the other hand, Xiong et al. in \cite{sparse_st, 6189245} use sparse representation for up-sampling video frame in low resolution. Key frames are selected as high resolution and the non-key frame are down-sampled in low resolution. High resolution version are recovered  using the learning-based super-resolution reconstruction and all frames of the video are encoded and decoded using H.264 encoder. For reconstruction a set of 2-D sub-dictionary pairs (High Resolution and Low resolution) and a 3-D dictionary pair (High Resolution and Low resolution) are created. First dictionary is trained with primitive frame patches and the second dictionary is trained with interpolated patches combined with the most matched patches in the neighbor training frame using K-SVD algorithm. This proposal shows improvements in coding efficiency in low bit-rate regions compared to H.264 encoder.\\

In the field of compressed video sensing, Azghan et al. present in \cite{7076640} a compressive sampling and    multihypothesis reconstruction strategy for video sequences. The video frames are grouped as reference and non-reference. Reference frame is divided into nonoverlapping blocks and it are vectorized 
 
In some articles combine the distributed video coding with compressing, in a proposal called Distributed Compressed Video Coding (DVCS). In \cite{} 